### 2015-02-22 fundamentals/impl.tex
reduced intro to mod software. specifically, this section was being a bit editorial

A modular, \acrfull{ABM} approach is ideal for solving complex, coupled,
physics-dependent supply chain problems involving material routing, facility
deployment, and regional and institutional hierarchies. Additionally, the choice to
build \Cyclus on open source libraries in modern programming languages enables
both remote and multiprocess execution on a number of platforms. This section begins by
describing the general design features that make \Cyclus both flexible and powerful:
cluster-ready software and dynamic libraries.  Next, the framework's
\gls{ABM} paradigm, which provides an expansion in performance beyond typical system dynamics
capabilities, is described, focusing on agent interchangeability and the
implementation of the region-institution-facility hierarchy.
Next, the discrete treatment of objects is discussed in terms of both
resources and materials and time via the \gls{DRE}.
Support for users and developers via the \Cycamore library of
archetypes and the experimental toolkit are also presented.
Lastly, the methods for quality assurance are outlined.

@@

The architecture of \Cyclus allows developers
to define nuclear fuel cycle agents and processes independent of the simulation
logic. To achieve this, agents are developed using the \Cyclus framework \gls{API}, a set of functions and protocols
which
assist in agent development and specify how agents should be defined.
This encapsulated `plug-in'
design choice provides two major benefits. First, analysts across research institutions can take advantage of the
simulation logic \gls{API} and archetype ecosystem when they apply \Cyclus to
their specific problem. This
mend-and-extend paradigm, common in modern software development, reduces
maintenance overhead and improves software robustness by protecting the core logic
from changes in the extensions.
The researcher can focus on creating or customizing nuclear
facility, institution, resource, and toolkit models within their specific area
of technical expertise. This extensibility, magnified by an open source
development process, frees the community of users to contribute desired
features, independent from the team of \Cyclus core developers.
Second, because \Cyclus uses a modular archetype approach, comparing two
archetypes is straightforward. For example, if an analyst would like
to compare the effect of using different models to determine the input fuel
composition for fast reactors, a variety of fuel fabrication archetypes can be
developed and interchanged while keeping the rest of the fuel cycle fixed
 to compare fuel fabrication designs.

@@

Two primary consequences arise from this structure. First, institutions are
nominally
responsible for deploying and decommissioning facilities. Accordingly, advanced
logic regarding building and decommissioning can be implemented on top of  
those behaviors inherited from the
\Class{Institution} interface. Second, the \Class{Facility} class implements the
\Class{Trader} interface, and thus institutions and regions, respectively, can
adjust the resource flow preferences of their managed facilities. Importantly,
this capability allows for the modeling of preferential regional trading
of resources (e.g., tariffs) as well as preferential institutional trading
(e.g., long-term contracts).

% the paragraph below muddies the concept of the RIF hierarchy
% (perhaps an extended footnote?)
% Either way, I prefer something other than ``provided explicitly''.

Although the \Cyclus kernel is designed around the concept of the \gls{RIF} hierarchy, 
it can handle hierarchies of arbitrary depth.  It is capable of
running a simulation without regions and institutions (i.e.  only facilities)
or a simulation having archetypes that are the parents of regions.  By
convention, institutions are mainly responsible for facility deployment, but
all archetypes have access to the agent deployment mechanism. \Cyclus enables
the developer to to implement agents that deploy copies of themselves, or that
schedule their own decommissioning.  Because regions, institutions, and
facilities are all just agents, they can all be implemented to exercise the
full set of features offered by the \Cyclus kernel.

@@

One such use case seeks to capture system vulnerability to nefarious
material diversion. Provenance and trade-history of distinct materials is the fundamental
information unit in such studies, and so this type of analysis requires
 discrete simulation of a
target facility and the individual materials modified within it.
Material risk analysis, therefore, demands that both facilities and materials
should be discretely modeled objects like those in \Cyclus.

@@

% although this abbreviation is provided by the glossary capability, I think
% the DRE is so important that it should be redefined here.

\subsubsection{Dynamic Resource Exchange (DRE)}

Since the \Cyclus simulation paradigm allows discrete agents, based on archetypes
about which the kernel has no knowledge, to enter 
the simulation at arbitrary times and
trade in discrete resources that are not defined \textit{a priori}, 
the logic engine defining resource interaction mechanisms
among agents is crucial. The \gls{DRE} is that critical logic engine on which \Cyclus
simulations are built.
As the \Cyclus supply-demand resolution framework,
the DRE must be able to support arbitrary facilities. Supporting the general
\Cyclus philosophy, facilities are treated as black boxes and a clear
supply-demand communication framework is defined.

@@

Suppliers then respond to the series of requests with a \textit{bid}. A bid
supplies a notion of the quantity and quality of a resource to match a
request. Suppliers may add an arbitrary number of constraints to accompany
bids. For example, an enriched \gls{UOX} supplier may be constrained by its current
inventory of natural uranium or its total capacity to provide enrichment (SWUs), and
attach such constraints to its bids. Any potential resource transfer may be denoted as
\textit{exclusive}. An exclusive transfer must either be met fully or not at all
in order to support concepts such as the trading of individual reactor
assemblies.

Finally, requesting facilities, institutions and regions may apply
\textit{preferences} to each potential request-bid pairing based on the proposed
resource transfer. Facilities can apply arbitrary complex logic to rank the bids 
that they have received, whether based on the quantity available in each bid or
on the quality of each bid, and the consequent implications of the physics behavior
of that facility. In addition, an institution can apply a higher preference to a
partner to which it is congenial; similarly, a region may negate any transfers
of material which have a higher uranium enrichment than is allowable.

@@

The \gls{DRE} is a novel simulation concept in the nuclear fuel cycle domain. It
provides a flexible supply-demand infrastructure, supporting dynamic flows of
resources between agents, even as those agents enter and leave the simulation, and 
even when those agents are defined by archetypes of arbitrary complexity. Trading 
between agents can be affected by both the
proposed quality of a resource and agent relationships through the use of
preferences. Accordingly, a wide range of possible effects can be
modeled, from capacitaty-limited fuel supply to international trade agreements.

@@

As illustrated in
Figure \ref{fig:simplesim}, the current \Cycamore release provides basic
functionality enabling simple fuel cycle analyses  As future contributions are
vetted, the capabilities in \Cycamore may grow.

@@

Integration tests combine multiple elements of the
\Cyclus interface and test that they work correctly with each other.  By analogy,
simply because the gears (units) are made correctly does not imply that the
clock (integration) will run smoothly, run at all, or give the correct time.
In \Cyclus and \Cycamore, integration tests are performed by running sample
simulations for scenarios that are sufficiently simple to predict the results and verifying 
that results match those predictions. A set of standard input files have thus been constructed.
Python is used to run the same set of \Cyclus simulations as a subprocess for each integration test. 
 The results are then inspected and compared via Nose \cite{pellerin_nose_2007}, a Python test framework.
In this way, \Cyclus code units are tested in the full context that they will be
executed. This category of testing is especially useful for ensuring that
major \Cyclus components are functioning as expected.

@@

Regression tests ensure significant unintended changes do not
occur over the course of \Cyclus development. Such a change is called a
\emph{regression} because the new version is almost always wrong.
Regression tests are implemented similarly to integration tests.
Nose is used to execute full \Cyclus simulations whose results
are then compared. In this category, however, the comparison is done against
the output of the same input file when run with a previous version of \Cyclus,
typically the last released version.
In some sense, regression tests are `dumb' in that they do
not care about the contents of a simulation being correct, only whether or not
it changed. They pick up glaring time-sensitive mistakes that may
not appear elsewhere, though they do not purport to make claims about the
quality of the physics modeled. Regression tests are primarily implemented
in \Cycamore because its archetypes are sophisticated enough
to make interesting input files. Only a handful ($<10$) of time steps are needed
for regression testing.

>>>>

A modular, \acrfull{ABM} approach is ideal for solving complex, coupled,
physics-dependent supply chain problems involving material routing, facility
deployment, and regional and institutional hierarchies. Additionally, the choice to
build \Cyclus on open source libraries in modern programming languages enables
both remote and multiprocess execution on a number of platforms. This section begins by
describing the general design features that make \Cyclus both flexible and powerful:
cluster-ready software and dynamic libraries.  Next, the framework has an
\gls{ABM} paradigm, which provides an expansion in performance beyond typical system dynamics
capabilities, is described, focusing on agent interchangeability and the
implementation of the region-institution-facility hierarchy.
Next, the discrete treatment of objects is discussed in terms of both
resources and materials and time via the \gls{DRE}.
Support for users and developers via the \Cycamore library of
archetypes and the experimental toolkit are also presented.
Lastly, the methods for quality assurance are outlined.

@@

The architecture of \Cyclus allows developers to define nuclear fuel cycle
agents and processes independent of the simulation logic. To achieve this,
agents are developed using the \Cyclus framework \gls{API}, a set of functions
and protocols which assist in agent development and specify how agents should be
defined.  This encapsulated `plug-in' design choice provides two major
benefits. First, analysts across research institutions can take advantage of the
simulation logic \gls{API} and archetype ecosystem when they apply \Cyclus to
their specific problem.  A researcher can focus on creating or customizing
nuclear facility, institution, resource, and toolkit models within their
specific area of technical expertise. Second, because \Cyclus uses a modular
archetype approach, comparing two archetypes is straightforward. For example, if
an analyst would like to compare the effect of using different models to
determine the input fuel composition for fast reactors, a variety of fuel
fabrication archetypes can be developed and interchanged while keeping the rest
of the fuel cycle fixed to compare fuel fabrication designs.

@@

Two primary consequences arise from this structure. First, institutions are
nominally
responsible for deploying and decommissioning facilities. Accordingly, advanced
logic regarding building and decommissioning can be obtained by inheriting
those behaviors from the
\Class{Institution} interface. Second, the \Class{Facility} class implements the
\Class{Trader} interface, and thus institutions and regions, respectively, can
adjust the resource flow preferences of their managed facilities. Importantly,
this capability allows for the modeling of preferential regional trading
of resources (e.g., tariffs) as well as preferential institutional trading
(e.g., long-term contracts).

Although concept of the \gls{RIF} hierarchy is provided explicitly, the \Cyclus kernel is
designed to handle hierarchies of arbitrary depth.  It is capable of
running a simulation without regions and institutions (i.e.  only facilities)
or a simulation having archetypes that are the parents of regions.  By
convention, institutions are mainly responsible for facility deployment, but
all archetypes have access to the agent deployment mechanism. \Cyclus enables
the developer to to implement agents that deploy copies of themselves, or that
schedule their own decommissioning.  Because regions, institutions, and
facilities are all just agents, they can all be implemented to exercise the
full set of features offered by the \Cyclus kernel.

@@

One such use case seeks to capture system vulnerability to nefarious
material diversion. Provenance and trade-history of distinct materials is the fundamental
information unit in such studies, and so this type of analysis requires
 discrete simulation of a
target facility and the individual materials modified within it.
Provenance and trade-history of distinct materials is the fundamental
information unit in such studies.
Material risk analysis, therefore, demands that both facilities and materials
should be discretely modeled objects like those in \Cyclus.

@@

\subsubsection{Dynamic Resource Exchange}

Since the \Cyclus simulation paradigm involves both discrete agents and
discrete resources, the logic engine defining resource interaction mechanisms
among agents is crucial. The \gls{DRE} is that critical logic engine on which \Cyclus
simulations are built.
As the \Cyclus supply-demand resolution framework,
the DRE must be able to support arbitrary facilities. Supporting the general
\Cyclus philosophy, facilities are treated as black boxes and a clear
supply-demand communication framework is defined.

@@

Suppliers then respond to the series of requests with a \textit{bid}. A bid
supplies a notion of the quantity and quality of a resource to match a
request. Suppliers may add an arbitrary number of constraints to accompany
bids. For example, an enriched \gls{UOX} supplier may supply both a natural uranium
and SWU constraint. Any potential resource transfer may be denoted as
\textit{exclusive}. An exclusive transfer must either be met fully or not at all
in order to support concepts such as the trading of individual reactor
assemblies.

Finally, requesting facilities, institutions and regions may apply
\textit{preferences} to each potential request-bid pairing based on the proposed
resource transfer. Therefore, an institution can apply a higher preference to a
partner to which it is congenial; similarly, a region may negate any transfers
of material which have a higher uranium enrichment than is allowable.

@@

The \gls{DRE} is a novel simulation concept in the nuclear fuel cycle domain. It
provides a flexible supply-demand infrastructure, supporting dynamic flows of
resources between agents. Trading between agents can be affected by both the
proposed quality of a resource and agent relationships through the use of
preferences. Accordingly, a wide range of possible effects can be
modeled, from capacitaty-limited fuel supply to international trade agreements.

@@

The current \Cycamore release provide basic functionality, As illustrated in
Figure \ref{fig:simplesim}, the current \Cycamore release provides basic
functionality enabling simple fuel cycle analyses  As future contributions are
vetted, the capabilities in \Cycamore may grow.

@@

Integration tests combine multiple elements of the
\Cyclus interface and test that they work correctly with each other.  By analogy,
simply because the gears (units) are made correctly does not imply that the
clock (integration) will run smoothly, run at all, or give the correct time.
In \Cyclus and \Cycamore, integration tests are performed by running sample
simulations and verifying that results are what would be expected ahead of
time. A set of standard input files have thus been constructed.
Python is used to run the same set of \Cyclus simulations as a subprocess for each integration test.  The results are then inspected and compared via Nose \cite{pellerin_nose_2007}, a Python test framework.
In this way, \Cyclus code units are tested in the full context that they will be
executed. This category of testing is especially useful for ensuring that
major \Cyclus components are functioning as expected.

@@

Regression tests ensure significant changes do not
occur over the course of \Cyclus development. Such a change is called a
\emph{regression} because the new version is almost always wrong.
Regression tests are implemented similarly to integration tests.
Nose is used to execute full \Cyclus simulations whose results
are then compared. In this category, however, the comparison is done against
the output of the same input file when run with a previous version of \Cyclus,
typically the last released version.
In some sense, regression tests are `dumb' in that they do
not care about the contents of a simulation being correct, only whether or not
it changed. They pick up glaring time-sensitive mistakes that may
not appear elsewhere, though they do not purport to make claims about the
quality of the physics modeled. Regression tests are primarily implemented
in \Cycamore because its archetypes are sophisticated enough
to make interesting input files. Only a handful ($<10$) of time steps are needed
for regression testing.
